---
title: "Fetch homozygous genotypes of inbred mouse strains"
output: BiocStyle::html_document
author: "Matthias Munz"
vignette: >
    %\VignetteIndexEntry{Fetch}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
---


```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>"
)
```

# Introduction
This **R** package provides methods for **genetic finemapping** in **inbred mice** by taking advantage of their **very high homozygosity rate** (>95%).

Method `fetch` allows to download homozygous genotypes of 37 inbred mouse strains for a given genetic region.

# Installation
```{r setup, eval=FALSE}
if(!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install("MouseFM")
```

# Loading package
```{r}
library(MouseFM)
```

# Example function calls
Fetch genotypes for region chr1:5000000-6000000.
```{r}
df = fetch("chr1", start=5000000, end=6000000)

df[1:10,]
```

View meta information
```{r}
comment(df)
```


# Output of Session Info
The output of `sessionInfo()` on the system
on which this document was compiled:
```{r}
sessionInfo()
```
